### 2018-02-13 manuscript/03_results.Rmd
Results: Update remaining results with new runs

For all traits except leaf lifespan, pairwise trait correlations were generally consistent in direction both globally and within each PFT (Fig.\ 4).
In particular, mass- and area-normalized traits were all positively correlated with each other and, respectively, positively and negatively correlated with SLA, both globally and within each PFT.
The same was generally true of correlations of mass-based traits with leaf lifespan, but correlations of leaf lifespan with area-normalized traits were more variable.
The correlation between $N_{area}$ and leaf lifespan was positive globally and for evergreen shrubs but negative for broadleaved deciduous trees and not significant for any other PFTs.
Similarly, the correlation between $P_{area}$ and leaf lifespan was positive for temperate broadleaved evergreen trees and needleleaved evergreen trees but negative for evergreen shrubs.
The correlation between leaf lifespan and $R_{d,area}$ significant and positive globally, but was not significant within any PFTs.
The correlations of leaf lifespan with $V_{c,max,area}$ and $J_{max,area}$ were negative for temperate broadleaved deciduous trees, but not significant for any other PFTs or globally.

A large number of pairwise trait correlations were not significant.
In some cases, this was driven by sample size (Fig.\ 1).
For instance, needleleaved deciduous trees were often the only PFT for which a correlation was not statistically significant.
In other cases, though, PFTs with smaller sample sizes had significant pairwise correlations while PFTs with much larger sample sizes had none.
For example, tropical broadleaved evergreen trees were relatively well-sampled for all traits, but none of their traits were well correlated with leaf lifespan.
Meanwhile, temperate broadleaved evergreen trees had significant correlations between leaf lifespan and SLA, $P_{area}$, and $R_{d,area}$.
In general, we observed fewer significant trait correlations among area-normalized traits than mass-normalized traits.

>>>>

For all traits except leaf lifespan, pairwise trait correlations were generally consistent in direction both globally and within each PFT (Fig.\ 4).
In particular, mass- and area-normalized traits were all positively correlated with each other and, respectively, positively and negatively correlated with SLA, both globally and within each PFT.
The same was generally true of correlations of mass-based traits with leaf lifespan, but correlations of leaf lifespan with area-normalized traits were more variable.
The correlation between $N_{area}$ and leaf lifespan was positive globally and for evergreen shrubs, tropical broadleaved deciduous trees, temperate needleleaved evergreen trees but negative for temperate and boreal broadleaved deciduous trees and not significant for any other PFTs.
Similarly, the correlation between $P_{area}$ and leaf lifespan was positive globally but negative for evergreen shrubs and not significant for any other PFTs.
The correlation between leaf lifespan and $R_{d,area}$ significant and negative globally, but was not significant within any PFTs.
The only significant correlations of leaf lifespan with $V_{c,max,area}$ and $J_{max,area}$ were negative for temperate broadleaved deciduous trees.

A large number of pairwise trait correlations were not significant.
In some cases, this was driven by sample size (Fig.\ 1).
For instance, needleleaved deciduous trees, the most undersampled PFT in our analysis, were often the only PFT for which a correlation was not statistically significant.
In other cases, though, PFTs with smaller sample sizes had significant pairwise correlations while PFTs with much larger sample sizes had none.
For example, tropical broadleaved evergreen trees were relatively well-sampled for all traits, but none of their area-normalized traits were significantly correlated with leaf lifespan.
In general, we observed fewer significant trait correlations among area-normalized traits than mass-normalized traits.
